Fast Fourier transformation of electromagnetic data for computationally expensive kernels

### 2021-04-23 ManuscriptTime.tex
Changes for Accepted version (#4)
- Add Zenodo DOI.
- Add png figures.

\documentclass[extra, camera,%
    % onecolumn,   % comment for two columns
    % referee,     % uncomment for double lines
    final,       % uncomment for changes
]{gji}
\usepackage{timet}

@@

% Change default colour of «changes» package
\definecolor{alizarin}{rgb}{0.82, 0.1, 0.26}
\definecolor{mygreen}{rgb}{0, .5, 0}
\setaddedmarkup{\color{mygreen}{\uline{#1}}}
\setdeletedmarkup{\color{alizarin}{\uwave{#1}}}

@@

% Own commands
\newcommand{\mr}[1]{\mathrm{#1}}
\newcommand{\emg}[2]{\texttt{emg#1#2}\xspace}
\newcommand{\empymod}{\texttt{empymod}\xspace}
\newcommand{\simpeg}{\texttt{SimPEG}\xspace}
\newcommand{\custem}{\texttt{custEM}\xspace}

% Remove once done
% \newcommand{\itodo}[1]{\todo[color=blue!40!white, inline]{\sffamily #1}}
% \newcommand{\mtodo}[1]{\todo[inline]{\sffamily #1}}
% \newcommand{\etodo}[1]{\todo[color=blue!40!white]{#1}}
\newcommand{\dul}[1]{\underline{\underline{#1}}}
\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\rmk}[1]{{\color{red}{#1}}}
\newcommand{\ohmm}{\ensuremath{\Omega\,}\text{m}\xspace}
\newcommand{\rtodo}{{\color{red}\texttt{TODO:}}\xspace}

@@

\date{Received 202Y MMMM DD; in original form 2020 June 30}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\volume{VVV}
\pubyear{202Y}

@@

The data that support the findings of this study are openly available at Zenodo
at \href{https://zenodo.org/badge/DOI/10.5281/zenodo.???????}{doi:
10.5281/zenodo.???????}. The data includes the scripts and instructions to
reproduce all results and figures.

\emph{Note to editors and reviewers: The data are NOT YET on Zenodo, we will
upload there the final versions and link the right DOI for the final
manuscript. Until then everything can be found on GitHub at
\href{https://github.com/empymod/article-TDEM}%
{github.com/empymod/article-TDEM}.}

>>>>

\documentclass[extra, camera,%
    % onecolumn,   % comment for two columns
    % referee,     % uncomment for double lines
    % final,       % uncomment for changes
]{gji}
\usepackage{timet}

@@

% Change default colour of «changes» package
% \definecolor{alizarin}{rgb}{0.82, 0.1, 0.26}
% \definecolor{mygreen}{rgb}{0, .5, 0}
% \setaddedmarkup{\color{mygreen}{\uline{#1}}}
% \setdeletedmarkup{\color{alizarin}{\uwave{#1}}}

@@

% Own commands
\newcommand{\mr}[1]{\mathrm{#1}}
\newcommand{\emg}[2]{\texttt{emg#1#2}\xspace}
\newcommand{\empymod}{\texttt{empymod}\xspace}
\newcommand{\simpeg}{\texttt{SimPEG}\xspace}
\newcommand{\custem}{\texttt{custEM}\xspace}
\newcommand{\ohmm}{\ensuremath{\Omega\,}\text{m}\xspace}

% Remove once done
% \newcommand{\itodo}[1]{\todo[color=blue!40!white, inline]{\sffamily #1}}
% \newcommand{\mtodo}[1]{\todo[inline]{\sffamily #1}}
% \newcommand{\etodo}[1]{\todo[color=blue!40!white]{#1}}
% \newcommand{\dul}[1]{\underline{\underline{#1}}}
% \newcommand{\ul}[1]{\underline{#1}}
% \newcommand{\rmk}[1]{{\color{red}{#1}}}
% \newcommand{\rtodo}{{\color{red}\texttt{TODO:}}\xspace}

@@

\date{Received 202Y MMMM DD; in original form 2020 June 30}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\volume{VVV}
\pubyear{2021}

@@

The data that support the findings of this study are openly available at Zenodo
at \href{https://doi.org/10.5281/zenodo.4710820}{doi: 10.5281/zenodo.4710820}.
The data includes the scripts and instructions to reproduce all results and
figures.
